### 2018-07-27 README.Rmd
minor tidying up - add isTRUE statments to if

We can use the function `process()` to take the derivative of this mass loss data, resulting in rate of mass loss over temperature data. To do so you simply need to specify the dataset, identify which columns contain temperature and mass loss data, and provide a value for the starting mass of the sample. The function defaults to temperature data in Celsius, but you can also modify to indicate the data is provided in Kelvin, by adding `temp_type = 'K'`.
```{r}
tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 16.85)
tmp
```

@@

You can see the full worked example in the vignette, which you can access on the [website](http://smwindecker.github.io/deconvolve/) or in R:
```{r}
vignette('deconvolve')
```

>>>>

We can use the function `process()` to take the derivative of this mass loss data, resulting in rate of mass loss over temperature data. To do so you simply need to specify the dataset, identify which columns contain temperature and mass loss data, and provide a value for the starting mass of the sample. The function defaults to temperature data in Celsius, but you can also modify to indicate the data is provided in Kelvin, by adding `temp_type = 'K'`.
```{r}
tmp <- process(juncus, temp = 'temp_C', mass = 'mass_loss', init_mass = 18.96)
tmp
```

@@

You can see the full worked example in the vignette, which you can access on the or in R:
```{r}
vignette('deconvolve')
```
